Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-14 icse/paper.tex
Contents

\subsection{Context Mapping}
After clones are detected, we map the context of these clones. We have identifier three properties of clones as their context: relation, location and contents. We identify categories for each of these properties, to get a detailed insight in the context of clones.

\subsubsection{Relation}
% The rationale for our categories regarding clone relations.
Clone instances in a clone class can have a relation with each other through inheritance. This relation has a big impact on how the clone should be refactored \cite{fontana2015duplicated}. We define the following categories to map the relation between clone instances in a clone class. These categories do not map external classes (classes outside the project, for instance belonging to a library) unless explicitly stated:
\begin{itemize}
    \item \textbf{Common Class}: All clone instances are in the same class.
    \begin{itemize}
        \item \textbf{Same Method}: All clone instances are in the same method.
        \item \textbf{Same Class}: All clone instances are in the same class.
    \end{itemize}
    \item \textbf{Common Hierarchy}: All clone instances are in the same inheritance hierarchy.
    \begin{itemize}
        \item \textbf{Superclass}: Clone instances reside in a class or its parent class.
        \item \textbf{Sibling Class}: All clone instances reside in classes with the same parent class.
        \item \textbf{Ancestor Class}: All clone instances reside in a class, or any of its recursive parents.
        \item \textbf{First Cousin}: All clone instances reside in classes with the same grandparent class.
        \item \textbf{Same Hierarchy}: All clone instances are part of the same inheritance hierarchy.
    \end{itemize}
    \item \textbf{Common Interface}: All clone instances are in classes that have the same interface.
    \begin{itemize}
        \item \textbf{Same Direct Interface}: All clone instances are in a class that have the same interface.
        \item \textbf{Same Class}: All clone instances are in an inheritance hierarchy that contains the same interface.
    \end{itemize}
    \item \textbf{Unrelated}: All clone instances are in classes that have the same interface.
    \begin{itemize}
        \item \textbf{No Direct Superclass}: All clone instances are in classes that have the Object class as parent.
        \item \textbf{No Indirect Superclass}: All clone instances are in a hierarchy that contains a class that has the Object class as parent.
        \item \textbf{External Superclass}: All clone instances are in classes the same external class as parent.
        \item \textbf{Indirect External Ancestor}: All clone instances are in a hierarchy that contains a class that has an external class as parent.
    \end{itemize}
\end{itemize}
Based on these relations, we determine where to place the cloned code when refactored. The code of clones that have a \textit{Common Class} relation can be refactored by placing the cloned code in this same class. The code of clones with a \textit{Common Hierarchy} relation can be placed in the intersecting class in the hierarchy (the class all clone instances have in common as an ancestor). The code of clones with a \textit{Common Interface} relation can be placed in the intersecting interface, but in the process has to become part of the classes' public contract. The code of clones that are \textit{Unrelated} can be placed in a newly created place: either a utility class, a new superclass abstraction or an interface.

\subsubsection{Contents}
% The rationale for our categories regarding clone contents.

\begin{enumerate}
  \item \textbf{Full Method/Constructor/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
  \item \textbf{Partial Method/Constructor:} A clone that spans (a part of) the body of a method/constructor.
  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods.
  \item \textbf{Only Fields:} A clone that spans only global variables.
  \item \textbf{Other:} Anything that does not match with above-stated categories.
\end{enumerate}

\subsection{Refactoring}
\subsubsection{Extract Method}
Show my categories to show what clones can be dealt with by method extraction.

>>>>

\subsection{Context Mapping}
After clones are detected, we map the context of these clones. We have identifier three properties of clones as their context: relation and contents. We identify categories for each of these properties, to get a detailed insight in the context of clones.

\subsubsection{Relation}
% The rationale for our categories regarding clone relations.
Clone instances in a clone class can have a relation with each other through inheritance. This relation has a big impact on how the clone should be refactored \cite{fontana2015duplicated}. We define the following categories to map the relation between clone instances in a clone class. These categories do not map external classes (classes outside the project, for instance belonging to a library) unless explicitly stated:
\begin{itemize}
    \item \textbf{Common Class}: All clone instances are in the same class.
    \begin{itemize}
        \item \textbf{Same Method}: All clone instances are in the same method.
        \item \textbf{Same Class}: All clone instances are in the same class.
    \end{itemize}
    \item \textbf{Common Hierarchy}: All clone instances are in the same inheritance hierarchy.
    \begin{itemize}
        \item \textbf{Superclass}: Clone instances reside in a class or its parent class.
        \item \textbf{Sibling Class}: All clone instances reside in classes with the same parent class.
        \item \textbf{Ancestor Class}: All clone instances reside in a class, or any of its recursive parents.
        \item \textbf{First Cousin}: All clone instances reside in classes with the same grandparent class.
        \item \textbf{Same Hierarchy}: All clone instances are part of the same inheritance hierarchy.
    \end{itemize}
    \item \textbf{Common Interface}: All clone instances are in classes that have the same interface.
    \begin{itemize}
        \item \textbf{Same Direct Interface}: All clone instances are in a class that have the same interface.
        \item \textbf{Same Class}: All clone instances are in an inheritance hierarchy that contains the same interface.
    \end{itemize}
    \item \textbf{Unrelated}: All clone instances are in classes that have the same interface.
    \begin{itemize}
        \item \textbf{No Direct Superclass}: All clone instances are in classes that have the Object class as parent.
        \item \textbf{No Indirect Superclass}: All clone instances are in a hierarchy that contains a class that has the Object class as parent.
        \item \textbf{External Superclass}: All clone instances are in classes the same external class as parent.
        \item \textbf{Indirect External Ancestor}: All clone instances are in a hierarchy that contains a class that has an external class as parent.
    \end{itemize}
\end{itemize}

Based on these relations, we determine where to place the cloned code when refactored. The code of clones that have a \textit{Common Class} relation can be refactored by placing the cloned code in this same class. The code of clones with a \textit{Common Hierarchy} relation can be placed in the intersecting class in the hierarchy (the class all clone instances have in common as an ancestor). The code of clones with a \textit{Common Interface} relation can be placed in the intersecting interface, but in the process has to become part of the classes' public contract. The code of clones that are \textit{Unrelated} can be placed in a newly created place: either a utility class, a new superclass abstraction or an interface.

\subsubsection{Contents}
% The rationale for our categories regarding clone contents.
The contents of a clone instance determine what refactoring techniques can be applied to refactor such clones. We define the following categories by which we analyze the contents of clones:
\begin{enumerate}
  \item \textbf{Full Method/Constructor/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
  \item \textbf{Partial Method/Constructor:} A clone that spans (a part of) the body of a method/constructor.
  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods.
  \item \textbf{Only Fields:} A clone that spans only global variables.
  \item \textbf{Other:} Anything that does not match with above-stated categories.
\end{enumerate}

\subsubsection{Full Method/Constructor/Class/Interface/Enumeration}
The categories denote that a full declaration (method, class, etc.) often denote redundancy and are often easy to refactor: one of both declarations is redundant and should be removed. Clones in the ``Partial Method/Constructor'' category can often be refactored using the ``Extract Method'' refactoring technique. Clones consisting of \textit{Several Methods} give a strong indication that cloned classes are missing some form of abstraction, or their abstraction is used inadequately. Clones consisting of \textit{Only Fields} often indicate data redundancy: different classes use the same data.

\subsection{Refactoring}
CloneRefactor can refactor clones using the ``Extract Method'' refactoring technique. In this section...

\subsubsection{Extract Method}
Show my categories to show what clones can be dealt with by method extraction.
